Finite Property Convex Elicitation Paper

### 2019-01-24 cvx-fin.tex
Added TFAE statements from Jessie's writeup and notation

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}

@@

@@

\begin{proposition}
  \raf{equivalence of possible definitions}
\end{proposition}

@@

\raf{The full characterization; optimality and monotonicity:}
\begin{theorem}
  A finite property $\Gamma:\R\toto\simplex$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
  \begin{enumerate}
  \item For all $r\in\R, p\in\simplex$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
  \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(\varphi(r))$.
  \end{enumerate}
\end{theorem}

>>>>

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}

@@

\subsection{Notation}
\begin{itemize}
	\item $\Y$ is the finite outcome space, and $n := |\Y|$.
	\item $\simplex$ is the set of distributions over $\Y$.
	\item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
	\item If $\gamma = \prop{\ell}$, then $\gamma:\simplex \toto \R$ is the property elicited by the loss $\ell: \R \to \reals^\Y$.
	\item $d$ is the dimension of the embedding space
	\item $L:\reals^d \to \reals^\Y$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$.
	\item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
	\item $\Gamma_u = \{ p \in \simplex : u \in \Gamma(p) \}$
	\item $\psi$ is the link function (see below)
	\item $\varphi:\R \to \reals^d$ is the embedding function
	\item $\trim(\Gamma)$ and $\strip(\Gamma)$
	\item $\eliccvx$, $\elicembed$, and $\elicpoly$
	\item $V$ and $B(P)$ as we get ready for later.
\end{itemize}

@@

\begin{definition}\label{def:strip-and-trim}
	\jessie{strip, trim}
	For $\Gamma:\simplex \toto \R'$, define $\strip(\Gamma) = \{\Gamma_r : r \in \R' \}$.
	If $\Gamma$ has a finite set of full-dimensional level sets that union to $\simplex$, there is a finite property $\gamma:\simplex \toto \R$ such that $\strip(\gamma) := \trim(\Gamma)$.
	\jessie{Fix without over-explaining.}
\end{definition}

\begin{proposition}\label{prop:optimal-reports-per-level-set}
	Let $\Gamma:\simplex\toto\reals^d$ be a non-degenerate (convex) elicitable property.

	The following are equivalent:
	\begin{enumerate}
		\item There is a nondegenerate, finite property $\gamma:\simplex\toto\R$ such that there is an injection $\varphi:\R\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds a finite $\gamma$).  
		\item $\trim(\Gamma)$ is finite.     
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.

	\end{enumerate}
\end{proposition}

\begin{proof}
	We proceed in a cycle to show $1 \implies 2 \implies 3 \implies 1 $.
	\begin{enumerate}
		\item [$1 \implies 2$]
		We know $\strip(\gamma) = \trim(\Gamma)$ (since $\varphi$ is an injection, and there is some intermediate property $\Gamma'$ such that $\Gamma' \preceq \Gamma$ and with a bijection $\phi:\Gamma'(p) \mapsto \gamma(p)$, so $\strip(\Gamma') = \strip(\gamma)$.) 
		As $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.

		\item [$2 \implies 3$]
		Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the level sets of $\trim(\Gamma)$ union to $\simplex$ by nondegneracy of $\Gamma$.

		\item[$3 \implies 1$]
		Construct $\R := \{[u] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
		The property $\gamma: p \mapsto \Gamma(p) \cap\R$ is then finite as $\R$ is finite.
		Taking $\varphi$ to be the identity, $\Gamma$ embeds this finite $\gamma$.
	\end{enumerate} 
\end{proof}

@@

\raf{The full characterization; optimality and monotonicity:}
\begin{theorem}
  A finite property $\Gamma:\simplex\toto\R$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
  \begin{enumerate}
  \item For all $r\in\R, p\in\simplex$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
  \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(\varphi(r))$.
  \end{enumerate}
\end{theorem}

### 2019-01-24 jessie-writeup/jw-holes-clarified.tex
Added TFAE statements from Jessie's writeup and notation

>>>>

\newpage
\section{Definitions for paper}
\begin{definition}
	Let $\gamma:\Delta_\Y \toto \R$ and $\Gamma:\Delta_\Y \toto \R'$ be elicitable properties.
	The property $\gamma$ refines $\Gamma$ if, for all $r \in \R$, there is an $r' \in \R'$ so that $\gamma_r \subseteq \Gamma_{r'}$.
	[Additionally, there is at least one $r \in \R$ and $r' \in \R'$ such that $\gamma_r \subsetneq \Gamma_{r'}$.]
\end{definition}
